\documentclass{vldb}



\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{balance}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{hyperref}



\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{problem}{Problem}

\newcommand{\mf}{\ensuremath{\mathfrak}}
\newcommand{\rv}{\ensuremath{\mathcal}}
\newcommand{\rb}{\ensuremath{\mathbf}}


\newenvironment{itemize0}
{ 
    \begin{itemize}
        \setlength{\itemsep}{1pt}
        \setlength{\parskip}{1pt}
        \setlength{\parsep}{1pt} 
}
{ \end{itemize}  }

\begin{document}

\title{Ziggy: Characterizing Query Results for Data Explorers}

\numberofauthors{2}
\author{
\alignauthor
    Thibault Sellam\\
    \affaddr{CWI}\\
    \affaddr{the Netherlands}
    \email{thibault.sellam@cwi.nl}
\alignauthor
Martin Kersten\\
    \affaddr{CWI}\\
    \affaddr{the Netherlands}
    \email{martin.kersten@cwi.nl}
}


\maketitle
\thispagestyle{empty}

\begin{abstract}
Data exploration has received much attention during the last few years. The aim
is to learn interesting new facts from a possibly unfamiliar database.
Typically, explorers operate by trial and error: they write a query, inspect
the results and refine their specifications accordingly. In this demo proposal,
we present Ziggy, a system to help them understand their query results. Ziggy's
aim is to complement an existing exploration system. It assumes that users
already have a query in mind, but they do not know what is interesting about
it. To assist them, it detects \emph{characteristic views}, that is, small sets
of columns on which the tuples in the results are different from that in the
rest of the database.  Thanks to these views, our explorers can understand why
their selection is unique and make more informed exploration decisions.
\end{abstract}

\input{Content}
\section{Acknowledgments}
This work was supported by the Dutch national program \\COMMIT.
\bibliographystyle{abbrv}
\small
\bibliography{Ziggy-demo}

\end{document}
