\documentclass{sig-alternate-2015}

%\clubpenalty=10000 
%\widowpenalty = 10000


\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumitem}
\usepackage{multirow}


\usepackage{color}
\usepackage{tabularx}
\usepackage[table]{xcolor}

\usepackage{framed}

\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem{lemma}{Lemma}

\newcommand{\mf}{\ensuremath{\mathfrak}}
\newcommand{\rv}{\ensuremath{\mathcal}}
\newcommand{\rb}{\ensuremath{\mathbf}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\nott}{\ensuremath{\overline{t}}}

\newenvironment{itemize0}
{ 
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt} 
}
{ \end{itemize}  }


\begin{document}

\title{``Hey Ziggy, What Am I Looking At?''\\
Describing Tuples for Data Explorers}

%\numberofauthors{3}
%\author{
%\alignauthor
%Thibault Sellam\\
%       \affaddr{CWI\\Amsterdam, the Netherlands}\\
%       \email{thibault.sellam@cwi.nl}
%\alignauthor
%Emmanuel M\"uller\\
%    \affaddr{HPI\\Potsdam, Germany}\\
%     \email{emmanuel.mueller@kit.edu}
%\alignauthor
%Martin Kersten\\
%       \affaddr{CWI\\Amsterdam, the Netherlands}\\
%       \email{martin.kersten@cwi.nl}
%}

\maketitle

\begin{abstract} 
The aim of data exploration is to get acquainted with an unfamiliar database.
Typically, explorers operate by trial and error: they submit a query, study the
result, and refine their query subsequently. In this paper, we investigate how
to help them understand their query results. In particular, we focus on medium
to high dimension spaces. If the database contains dozens or hundreds of
columns, which variables should they inspect? Our approach is the following: we
detect subspaces inside which the users' selection has an unusual distribution
compared to the rest of the database. From this idea, we built Ziggy, a tuple
description engine. Ziggy can detect informative subspaces, but it can also
explain why it recommends them, using natural language and visualizations. Thus
users are engaged in a veritable conversation with their data exploration tool.
We first present the general problem of characterizing tuples with multiple
views. We then describe Ziggy in detail. Finally, we showcase our system with a
use case and evaluate it with a wide range of real and synthetic data.
\end{abstract}


\category{H.2.8}{Database Applications}{Data mining}
\keywords{Data exploration, subspace search, feature selection}

\input{Content}

\bibliographystyle{abbrv}
\balance
\bibliography{MME}
\end{document}
