\documentclass{vldb}


%\clubpenalty=10000 
%\widowpenalty = 10000


\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumitem}
\usepackage{multirow}


\usepackage{color}
\usepackage{tabularx}
\usepackage[table]{xcolor}

\usepackage{framed}

\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem{lemma}{Lemma}

\newcommand{\mf}{\ensuremath{\mathfrak}}
\newcommand{\rv}{\ensuremath{\mathcal}}
\newcommand{\rb}{\ensuremath{\mathbf}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\nott}{\ensuremath{\overline{t}}}

\newenvironment{itemize0}
{ 
    \begin{itemize}
        \setlength{\topsep}{0pt}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt} 
}
{ \end{itemize}  }


\begin{document}

\title{Fast, Explainable View Detection\\ to Characterize Exploration Queries}

\numberofauthors{2}
\author{
\alignauthor
Thibault Sellam\\
       \affaddr{CWI\\Amsterdam, the Netherlands}\\
       \email{thibault.sellam@cwi.nl}
\alignauthor
%Emmanuel M\"uller\\
%    \affaddr{HPI\\Potsdam, Germany}\\
%     \email{emmanuel.mueller@kit.edu}
%\alignauthor
Martin Kersten\\
       \affaddr{CWI\\Amsterdam, the Netherlands}\\
       \email{martin.kersten@cwi.nl}
}

\maketitle

\begin{abstract} 
The aim of data exploration is to get acquainted with an unfamiliar
database.  Typically, explorers operate by trial and error: they submit a
query, study the result, and refine their query subsequently. In this
paper, we investigate how to help them understand their query results.  In
particular, we focus on medium to high dimension spaces: if the database
contains dozens or hundreds of columns, which variables should they
inspect? We propose to detect subspaces in which the users' selection is
different  from the rest of the database. From this idea, we built Ziggy, a
tuple description engine.  Ziggy can detect informative subspaces, and it
can explain why it recommends them, with visualizations and natural
language.  It can cope with mixed data, missing values, and it penalizes
redundancy. Finally, expe\-riments reveal that it is up to
an order of magnitude faster than state-of-the-art feature selection
algorithms, at minimal accuracy costs.
\end{abstract}


%\category{H.2.8}{Database Applications}{Data mining}
%\keywords{Data exploration, subspace search, data description}

\input{Content}

%\section{Acknowledgements}
%This publication was supported by the Dutch national program COMMIT.

\bibliographystyle{abbrv}
\balance
\bibliography{MME}
\end{document}
